%===========================%
%        YITANG GAO        %
%===========================%
\documentclass[11pt]{article}

% ---------- Packages ----------
\usepackage[margin=0.8in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{titlesec}
\usepackage[T1]{fontenc}
\usepackage{newtxtext}   % Times-like serif for a formal look
\usepackage{microtype}

% ---------- Section styling (bold caps + rule) ----------
\titleformat{\section}{\bfseries\Large}{}{0pt}{}[\vspace{2pt}\titlerule]
\titlespacing*{\section}{0pt}{8pt plus 2pt minus 2pt}{6pt}

% ---------- Global spacing ----------
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
% Tight spacing INSIDE entries (title→bullets), normal line spacing for bullets
\setlist[itemize]{leftmargin=*, topsep=0pt, partopsep=0pt, parsep=0pt, itemsep=2pt}

% ---------- Entry helpers ----------
% Org + location line
\newcommand{\orgloc}[2]{\noindent\textbf{#1}\hfill #2\\}

% Role + date line — tighten space BEFORE bullets to remove the "red gap"
\newcommand{\roledate}[2]{\textit{#1}\hfill #2\\[-11pt]}
% Education role/date — keep slightly more room so CGA line doesn't collide
\newcommand{\roledateedu}[2]{\textit{#1}\hfill #2\\[0pt]}

% Gap BETWEEN entries (the "green gap"): visible but compact
\newcommand{\entrygap}{\vspace{12pt}}

%===========================%
\begin{document}

% ---------- Header ----------
{\fontsize{20}{22}\selectfont\textbf{YITANG GAO}}\\[1pt]
Hong Kong SAR \,|\, +852 5449-7757 \,|\, \href{mailto:ygaocb@connect.ust.hk}{ygaocb@connect.ust.hk}

\vspace{4pt} % clear gap before first section (similar to section spacing)

%===========================%
\section*{EDUCATION}

\orgloc{The Hong Kong University of Science and Technology (HKUST)}{Hong Kong SAR}
\roledateedu{BEng in Computer Science}{Sep 2022--Jun 2026 (expected)}
CGA: \textbf{4.126/4.30};  Rank: \textbf{2/145};  Dean’s List every term.\\
TOEFL iBT: \textbf{108}.\\
Selected Coursework: Artificial Intelligence; Machine Learning; Large-Scale ML for Foundation Models;\\
Big Data Mining/Management; Data Visualization; OOP \& Data Structures; Algorithms; Operating Systems;\\
Software Engineering; Computer Organization; Linear Algebra; Probability and Statistics.

\entrygap

\orgloc{Cornell University}{Ithaca, NY}
\roledateedu{Visiting Research Student, Database Systems Lab}{Jun--Aug 2025}

\vspace{-10pt} % Make it tighter

%===========================%
\section*{RESEARCH EXPERIENCE}

\orgloc{HKUST LONG Group}{Hong Kong SAR}
\roledate{Final Year Thesis (advisor: Prof.\ Long Chen)}{Sep 2025--Present}
\begin{itemize}
  \item Investigate inference-time classifier-free guidance for autoregressive LMs.
  \item Design decoding/steering techniques to reduce hallucinations.
  \item Build long-context eval harnesses; plan guidance-scaling ablations.
\end{itemize}

\entrygap

\orgloc{Cornell University — Database Systems Lab}{Ithaca, NY}
\roledate{Research Intern (advisor: Prof.\ Sainyam Galhotra)}{Jun--Nov 2025}
\begin{itemize}
  \item \textit{Auto Pruned Retriever} (VLDB submission, under review).
  \item Co-develop token/latency‑efficient RAG via a persistent \emph{reasoning subgraph}.
  \item Engineer edge‑space retrieval + top‑\(k\) frontier sentence encodings with top‑\(m\) re‑rank; \emph{per abstract}: similar accuracy with \(\sim\)1/20 LightRAG tokens and \(\sim\)1/3 generation latency.
  \item Implement scalable causal discovery algorithm for the SEEKER project.
\end{itemize}

\entrygap

\orgloc{HKUST Accounting Department}{Hong Kong SAR}
\roledate{Undergraduate Research Assistant (advisor: Prof.\ Yue Zheng)}{Aug--Oct 2024}
\begin{itemize}
  \item Engineer OCR\(\rightarrow\)DB pipeline for 657 noisy/low‑res scanned complaints.
  \item Integrate Tesseract with heuristic post‑processing to extract \texttt{[file]–[keyword]–[text]} triplets; reduce complexity from \(O(n^4)\) to \(O(n^2)\); speedup \(\sim 20\times\) (days\(\rightarrow\)hours).
\end{itemize}

\entrygap

\orgloc{HKUST NLP Group}{Hong Kong SAR}
\roledate{Undergraduate Research Assistant (advisor: Prof.\ Junxian He)}{Jan--May 2024}
\begin{itemize}
  \item \textit{Long as a Tale: Unlocking Long‑Video Context in VLMs with Hour‑long Data.}
  \item Co‑design and implement hour‑long data pipeline: world‑knowledge taxonomy (6 categories/37 sub‑categories) \(\rightarrow\) YouTube retrieval \(\rightarrow\) three‑stage filtering (metadata: 20–60 min, \(\ge\)100 likes/\(\ge\)1{,}000 views; subtitle density: \(\ge\)100 chars/min, English; motion: CLIP cosine non‑similarity \(\ge\)0.8 for \(\ge\)50\% frames); curate \(\sim\)4.5K long videos.
  \item Script subtitle\(\rightarrow\)description conversion: chunking + metadata‑aware LLM rephrasing; standardize prompts; produce \(\sim\)2.7K‑token descriptions/video; ensure reproducibility.
  \item Set up long‑context training/eval: text‑only warm‑up to 224K context (RoPE \(\theta=10^9\)), 400‑frame video training; automate V‑NIAH, Video‑MME, MLVU, LVBench runs; \emph{paper outcomes}: +6.0 (Video‑MME long), +5.8 (medium), +0.7 (short), +3.4 (MLVU), +4.6 (LVBench); robust retrieval up to 1,200 frames.
\end{itemize}



%===========================%
\section*{TEACHING EXPERIENCE}

\orgloc{HKUST — COMP2211 \emph{Exploring Artificial Intelligence}}{Hong Kong SAR}
\roledate{Undergraduate Teaching Assistant}{Jul--Aug 2024 \& Jul--Aug 2025}
\begin{itemize}
  \item \textbf{Designed} labs with background notes, step-by-step instructions, reference solutions, and \textbf{autograders}; \textbf{held} office hours (\(\sim\)200 students).
\end{itemize}

\entrygap

\orgloc{HKUST — COMP1023 \emph{Introduction to Python}}{Hong Kong SAR}
\roledate{Undergraduate Teaching Assistant}{Sep--Dec 2024}
\begin{itemize}
  \item \textbf{Created} beginner-friendly labs with interactive UIs and \textbf{autograders}; \textbf{converted} coding tasks into small game-like projects (\(\sim\)800 students/term).
\end{itemize}

\entrygap

\orgloc{HKUST — COMP2012 \emph{OOP \& Data Structures}}{Hong Kong SAR}
\roledate{Undergraduate Teaching Assistant}{Jan--May 2024}
\begin{itemize}
  \item \textbf{Led} lab sections (\(\sim\)90 students per session), \textbf{demoed} data-structure implementations, and \textbf{answered} live Q\&A.
\end{itemize}

%===========================%
\section*{PROJECTS \& TRAINING}

\orgloc{Independent Quantitative Research}{Hong Kong SAR}
\roledate{Personal project}{Jul 2024--Sep 2025}
\begin{itemize}
  \item \textbf{Built} an equity stack: ingest daily/hourly data (e.g., \texttt{yfinance}) into \textbf{SQLite} then \textbf{ClickHouse}; \textbf{implemented} factor mining and backtesting with Python+\emph{PyO3}/Rust.
  \item \textbf{Researched} and \textbf{combined} published factors; \textbf{tested} equal-weight, market-neutral portfolios; \textbf{standardized} cleaning and universe rules.
\end{itemize}

\entrygap

\orgloc{LSE Summer School}{London, UK}
\roledate{Fixed Income Securities \& Debt Markets}{Jul--Aug 2023}

\orgloc{Fudan University Winter School}{Shanghai, China}
\roledate{Probability, Statistics \& Risk Management}{Dec 2022--Jan 2023}

%===========================%
\section*{HONORS \& AWARDS}

\noindent HKSAR Government Scholarship \hfill 2024--2026\\
Asia-Pacific Economic Cooperation Scholarship \hfill 2024--2026\\
Cornell IRIS Summer Scholarship \hfill 2025\\
HKUST SENG International Summer Research Sponsorship \hfill 2025\\
HKUST UROP Support Grant \hfill 2024\\
Extra Mile Charity Foundation Scholarship \hfill 2023--2024\\
University Scholarship Scheme for Continuing UG Students \hfill 2023--2024\\
HKUST Study Abroad Grant \hfill 2023\\
HKSAR Government Scholarship Fund — Talent Development Scholarship \hfill 2023--2024\\
Dean’s List (every semester) \hfill 2022--2025

%===========================%
\section*{SKILLS \& INTERESTS}

\textbf{Programming:} Python, Java, C/C++, SQL, Bash, HTML, \LaTeX \\
\textbf{Libraries/Tools:} PyTorch, Hugging Face, Pandas, OpenCV, Docker, Git, Linux \\
\textbf{Research interests:} Inference-time control of LMs; efficient \& multimodal AI; long-context modeling; data mining \\
\textbf{Interests:} Piano (\textbf{Level 10} certificate), music, hiking/outdoors, cooking

\end{document}
